\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-26 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\medskip
Numerical simulation was performed in slightly modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10. Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.

\medskip
Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.

\medskip
%Permeability values have been prescribed in the formation following a simple quadrant heterogenous model that will give the cross-flow that is expected in such a system. 
\red{(PLEASE REVISE THE PARAGRAPH ... AND YOU HAVEN'T ADDRESSED MY PREVIOUS COMMENTS ....)}
The flow profile follows the same behaviour with the experimental work of \citet{evans_1994}. In both cases the flow will not follow the standar source-sink behaviour while the mobility ratio (or VR) is playing a crucial role for these flows. The main difference between these two works is that by introducing an unstructured mesh the flow patterns are not only verified but also there is a more accurate descriptions during the development of the flow.

\medskip
In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations. Following a different set-up the idea is to validate the existance of cross flow and along with another region of different permeability.There is a comparison between the $VR=1$ and $VR=10$ case and the reason was to imply the same domain, boundary and initial conditions and number of elements to underastand how the cross-flow will develop. The purpose of these two cases was to verify that the model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.

>>>>

Numerical simulation was performed in slightly modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10. Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.

Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}. The main difference between these two works is that by introducing an unstructured mesh the flow patterns are not only verified but also there is a more accurate descriptions during the development of the flow. \red{(???? THE TWO PAPERS ARE EXPERIMENTAL ... THIS SENTENCE DOES NOT MAKE ANY SENSE ... PLEASE READ IT THROUGH !!)}

%Permeability values have been prescribed in the formation following a simple quadrant heterogenous model that will give the cross-flow that is expected in such a system. 
\red{(PLEASE REVISE THE PARAGRAPH ... AND YOU HAVEN'T ADDRESSED MY PREVIOUS COMMENTS ....)}
In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations. Following a different set-up the idea is to validate the existance of cross flow and along with another region of different permeability.There is a comparison between the $VR=1$ and $VR=10$ case and the reason was to imply the same domain, boundary and initial conditions and number of elements to underastand how the cross-flow will develop. The purpose of these two cases was to verify that the model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.
